### 2021-03-04 paper2/appendix.tex
Fix all kinds of small problems

\begin{table}[tp]
\caption{INN architecture used for each dataset.}
\label{tab:inn_architectures}
\centering
\begin{tabular}{l@{\extracolsep{1cm}}llllll}
\toprule
\multicolumn{1}{l}{Dataset} & Levels & Level depth & Coupling channels & Input to discriminator(s) \\ \midrule
UCI Adult                   & 1      & 1     & 35       & Null-samples       \\
cMNIST                      & 3      & 16     & 512      & Encodings               \\
CelebA                      & 3      & 32     & 512      & Encodings        \\ \bottomrule
\end{tabular}
\end{table}

\begin{table}[tp]
\caption{cVAE encoder architecture used for each dataset. The decoder architecture in each case mirrors that of its encoder counterpart through use of transposed convolutions. For the adult dataset we apply $\ell_2$ and cross-entropy losses to the reconstructions of the continuous features and discrete features, respectively.}
\label{tab:vae_architectures}
\centering
\begin{tabular}{l@{\extracolsep{1cm}}lllll}
\toprule
Dataset   & Initial channels & Levels & $\beta$ & Recon. loss \\
\midrule
UCI Adult & 35               & --     & 0       & $\ell_2$ + CE\\
cMNIST    & 32               & 4      & 0.01    & $\ell_2$ \\
CelebA    & 32               & 5      & 1       & $\ell_1$ \\ 
\bottomrule
\end{tabular}
\end{table}

\subsection{Additional results}\label{sec:additional-results}
\paragraph{Detailed results for UCI Adult dataset.}
This census data is commonly used to evaluate models focused on algorithmic fairness.
Following convention, we designate ``gender'' as the $s$ and whether an individual's salary is \$50,000 or greater as $y$.
We show the performance of our approach in comparison to baseline approaches in Fig.~\ref{fig:big-adult-chart}.
We evaluate the performance of all models for mixing factors ($\eta$) of value $\{0, 0.1, ..., 1\}$. 
Results shown in Fig.~\ref{fig:big-adult-chart} show that whilst our model fails to surpass the baseline models in terms of accuracy for the balanced case (and those close to it), we match or exceed the baseline as $\eta $ moves the dataset to a more imbalanced setting. In terms of fairness metrics,  our approach generally outperforms the baseline models regardless of $\eta$.

@@

\paragraph{Multinomial sensitive attributes.}
In addition to binary sensitive attribute $s$,
we also investigate multinomial $s$ in the CelebA dataset.
First, we do experiments with hair color, where $s$ has three possible values:
blond hair, brown hair and black hair.
The other experiment is with a combination of age and gender,
where $s$ has four possible values, each of which is a combination of a gender and an age:
Young/Female, Young/Male, Old/Female and Old/Male.
To evaluate the fairness for multinomial $s$, we use the Hirschfeld-Gebelein-R\'enyi Maximum Correlation Coefficient (HGR) \citep{mary2019fairness} that is defined on the domain $[0, 1]$ and gives $\text{HGR}(Y,S)=0$ iff $Y \perp S$
and 1 if there is a deterministic function to map between them.
Results can be found in Figure~\ref{fig:multi-s}.\\

@@

\begin{table}[tbp]
    \caption{
        Additional fairness metrics for the experiments on the CelebA dataset (Fig. 5 from the main text).
        \emph{TPR diff.} refers to the difference in true positive rate.
        \emph{TNR diff.} refers to the difference in true negative rate.
        \textsc{Left:} $\eta = 0$. \textsc{Right:} $\eta=1$.
    }
    \label{tab:my_label}
    \resizebox{.49\textwidth}{!}{
    \begin{tabular}{lrrrr}
\toprule
     Method &  Accuracy &  DP diff &  TPR diff &  TNR diff \\
\midrule
      cFlow &      0.83 &     0.10 &      0.15 &      0.25 \\
       cVAE &      0.82 &     0.05 &      0.09 &      0.18 \\
        CNN &      0.61 &     0.63 &      0.70 &      0.64 \\
 Ln2L &      0.52 &     0.00 &      0.00 &      0.00 \\
\bottomrule
\end{tabular}}
\hfill
\resizebox{.49\textwidth}{!}{
\begin{tabular}{lrrrr}
\toprule
     Method &  Accuracy &  DP diff &  TPR diff &  TNR diff \\
\midrule
      cFlow &      0.82 &     0.33 &      0.28 &      0.21 \\
       cVAE &      0.81 &     0.16 &      0.10 &      0.05 \\
        CNN &      0.67 &     0.75 &      0.66 &      0.76 \\
Ln2L &      0.51 &     0.08 &      0.06 &      0.09 \\
\bottomrule
\end{tabular}}
\end{table}
\paragraph{Additional fairness metrics.}
In addition to \emph{DP diff}, we report here the result from other fairness measures.
These results are from the same setup as those reported in the main paper.
We report the difference in true positive rates (TPR) between the two groups (male and female), which corresponds to a measure of Equality of Opportunity,
and the difference in true negative rates (TNR) between the two groups.

@@

\subsection{Qualitative Results for CelebA}\label{sec:qual-results-celeba}
\noindent Learning a representation alongside its inverse mapping, be it approximate or exact, enables us to probe the behaviour of the model that produced it,
and any biases it may have implicitly captured due to entanglement between the sensitive attribute and other attributes present in the data.
We highlight a few examples of such biases manifesting in the cFlow model's CelebA null-samples in Fig.~\ref{fig:celeba_cflow_suppmat}. In these cases, makeup and hair style have been inadvertently modified during the null-sampling due to the tight correlation between these two attributes and the sensitive attribute, gender, to which we had aimed to make our representations invariant. Additionally, in all highlighted images, the skin tone has changed: from male to gender-neutral, the skin becomes lighter and from female to gender-neutral, the skin becomes darker; in the change from male to gender-neutral, glasses are also often removed.
As the model cannot know that the label is meant to only refer to gender, and not to these other (correlated) attributes,
the links cannot be disentangled by the model.
However, the advantage of our method is that we can at least identify such biases due to the interpretability that comes with the representations being in the data domain.

@@

The results for the range of $\sigma$ values are shown in Fig.~\ref{fig:cmnist-transfer}. Unsurprisingly, the performance of both models suffers when the representative and test sets do not completely correspond. However, the cFlow model consistently outperforms the cVAE model, with the gap increasing as the bias decreases.
Although some colour information is retained in the cFlow null-samples, symptomatic of an imperfect transfer, semantic information is almost entirely retained as well.
Conversely, the cVAE is very much flawed in this respect; as can be seen in the bottom row of Fig.~\ref{fig:cmnist-transfer}, for some samples, semantic information is degraded to the point of the digit's identity being altered. As a result of this semantic degradation, the performance of the downstream classifier is curtailed by the noisiness of the digit's identity and is relatively unchanging across $\sigma$-values, in contrast to the monotonic improvement of that achieved on the cFlow null-samples.
% \begin{figure}
%   \includegraphics[width=0.6\textwidth]{./Figures/nosinn_cmnist_transfer.pdf}
%   \caption{
%      Results for transfer learning experiments on cMNIST.
%   }%
%   \label{fig:cmnist-transfer}
% \end{figure}

>>>>

\begin{table}[tp]
\caption{INN architecture used for each dataset.}
\label{tab:inn_architectures}
\centering
\begin{tabular}{lllll}
\toprule
Dataset & Levels & Level depth & Coupl. chan. & Input to discr. \\ \midrule
UCI Adult                   & 1      & 1     & 35       & Null-samples       \\
cMNIST                      & 3      & 16     & 512      & Encodings               \\
CelebA                      & 3      & 32     & 512      & Encodings        \\ \bottomrule
\end{tabular}
\end{table}

\begin{table}[tp]
\caption{cVAE encoder architecture used for each dataset. The decoder architecture in each case mirrors that of its encoder counterpart through use of transposed convolutions. For the adult dataset we apply $\ell_2$ and cross-entropy losses to the reconstructions of the continuous features and discrete features, respectively.}
\label{tab:vae_architectures}
\centering
\begin{tabular}{lllll}
\toprule
Dataset   & Initial channels & Levels & $\beta$ & Recon. loss \\
\midrule
UCI Adult & 35               & --     & 0       & $\ell_2$ + CE\\
cMNIST    & 32               & 4      & 0.01    & $\ell_2$ \\
CelebA    & 32               & 5      & 1       & $\ell_1$ \\ 
\bottomrule
\end{tabular}
\end{table}

\subsection{Additional results}\label{sec:additional-results}
\paragraph{Detailed results for UCI Adult dataset.}
This census data is commonly used to evaluate models focused on algorithmic fairness.
Following convention, we designate ``gender'' as the $s$ and whether an individual's salary is \$50,000 or greater as $y$.
We show the performance of our approach in comparison to baseline approaches in fig.~\ref{fig:big-adult-chart}.
We evaluate the performance of all models for mixing factors ($\eta$) of value $\{0, 0.1, ..., 1\}$. 
Results shown in fig.~\ref{fig:big-adult-chart} show that whilst our model fails to surpass the baseline models in terms of accuracy for the balanced case (and those close to it), we match or exceed the baseline as $\eta $ moves the dataset to a more imbalanced setting. In terms of fairness metrics,  our approach generally outperforms the baseline models regardless of $\eta$.

@@

\paragraph{Multinomial sensitive attributes.}
In addition to binary sensitive attribute $s$,
we also investigate multinomial $s$ in the CelebA dataset.
First, we do experiments with hair color, where $s$ has three possible values:
blond hair, brown hair and black hair.
The other experiment is with a combination of age and gender,
where $s$ has four possible values, each of which is a combination of a gender and an age:
Young/Female, Young/Male, Old/Female and Old/Male.
To evaluate the fairness for multinomial $s$, we use the Hirschfeld-Gebelein-R\'enyi Maximum Correlation Coefficient (HGR) \citep{mary2019fairness} that is defined on the domain $[0, 1]$ and gives $\text{HGR}(Y,S)=0$ iff $Y \perp S$
and 1 if there is a deterministic function to map between them.
Results can be found in figure~\ref{fig:multi-s}.\\

@@

\begin{table}[tbp]
    \caption{
        Additional fairness metrics for the experiments on the CelebA dataset (fig.~\ref{fig:celeba-multiplot} from the main text).
        \emph{TPR diff.} refers to the difference in true positive rate.
        \emph{TNR diff.} refers to the difference in true negative rate.
        \textsc{Left:} $\eta = 0$. \textsc{Right:} $\eta=1$.
    }
    \label{tab:my_label}
    \resizebox{.49\textwidth}{!}{
    \begin{tabular}{lrrrr}
\toprule
     Method &  Accuracy &  DP diff &  TPR diff &  TNR diff \\
\midrule
      cFlow &      0.83 &     0.10 &      0.15 &      0.25 \\
       cVAE &      0.82 &     0.05 &      0.09 &      0.18 \\
        CNN &      0.61 &     0.63 &      0.70 &      0.64 \\
 Ln2L &      0.52 &     0.00 &      0.00 &      0.00 \\
\bottomrule
\end{tabular}}
\hfill
\resizebox{.49\textwidth}{!}{
\begin{tabular}{lrrrr}
\toprule
     Method &  Accuracy &  DP diff &  TPR diff &  TNR diff \\
\midrule
      cFlow &      0.82 &     0.33 &      0.28 &      0.21 \\
       cVAE &      0.81 &     0.16 &      0.10 &      0.05 \\
        CNN &      0.67 &     0.75 &      0.66 &      0.76 \\
Ln2L &      0.51 &     0.08 &      0.06 &      0.09 \\
\bottomrule
\end{tabular}}
\end{table}
\paragraph{Additional fairness metrics.}
In addition to \emph{DP diff}, we report here the result from other fairness measures.
These results are from the same setup as those reported in the main paper.
We report the difference in true positive rates (TPR) between the two groups (male and female), which corresponds to a measure of Equality of Opportunity,
and the difference in true negative rates (TNR) between the two groups.

@@

\subsection{Qualitative Results for CelebA}\label{sec:qual-results-celeba}
\noindent Learning a representation alongside its inverse mapping, be it approximate or exact, enables us to probe the behaviour of the model that produced it,
and any biases it may have implicitly captured due to entanglement between the sensitive attribute and other attributes present in the data.
We highlight a few examples of such biases manifesting in the cFlow model's CelebA null-samples in fig.~\ref{fig:celeba_cflow_suppmat}. In these cases, makeup and hair style have been inadvertently modified during the null-sampling due to the tight correlation between these two attributes and the sensitive attribute, gender, to which we had aimed to make our representations invariant. Additionally, in all highlighted images, the skin tone has changed: from male to gender-neutral, the skin becomes lighter and from female to gender-neutral, the skin becomes darker; in the change from male to gender-neutral, glasses are also often removed.
As the model cannot know that the label is meant to only refer to gender, and not to these other (correlated) attributes,
the links cannot be disentangled by the model.
However, the advantage of our method is that we can at least identify such biases due to the interpretability that comes with the representations being in the data domain.

@@

The results for the range of $\sigma$ values are shown in fig.~\ref{fig:cmnist-transfer}. Unsurprisingly, the performance of both models suffers when the representative and test sets do not completely correspond. However, the cFlow model consistently outperforms the cVAE model, with the gap increasing as the bias decreases.
Although some colour information is retained in the cFlow null-samples, symptomatic of an imperfect transfer, semantic information is almost entirely retained as well.
Conversely, the cVAE is very much flawed in this respect; as can be seen in the bottom row of fig.~\ref{fig:cmnist-transfer}, for some samples, semantic information is degraded to the point of the digit's identity being altered. As a result of this semantic degradation, the performance of the downstream classifier is curtailed by the noisiness of the digit's identity and is relatively unchanging across $\sigma$-values, in contrast to the monotonic improvement of that achieved on the cFlow null-samples.
% \begin{figure}
%   \includegraphics[width=0.6\textwidth]{./Figures/nosinn_cmnist_transfer.pdf}
%   \caption{
%      Results for transfer learning experiments on cMNIST.
%   }%
%   \label{fig:cmnist-transfer}
% \end{figure}

### 2021-03-04 paper3/paper3.tex
Fix all kinds of small problems

%\icmltitle{Learning with Perfect Bags:\\
%Addressing Hidden Stratification with Zero Labelled Data}
\textsc{Authors}:\\
Thomas Kehrenberg$^1$, Viktoriia Sharmanska$^1$, Myles Bartlett$^1$, and Novi Quadrianto$^1$ \\
\textsc{Affiliations}:\\
$^1$ Predictive Analytics Lab (PAL), University of Sussex, Brighton, UK\\
\textsc{Conference}:\;\; Submitted to \textit{Internation Conference on Machine Learning} (ICML), 2021 \\
% \textsc{DOI}:\;\;10.3389/frai.2020.00033
\textsc{Note}:\;\;The appendix has been included as section~\ref{sec:zsf-appendix}.

@@

\section{Related work.}
We describe related work in two areas: zero-shot learning and semi-supervised learning.
%and disentangled representation learning.

>>>>

%\icmltitle{Learning with Perfect Bags:\\
%Addressing Hidden Stratification with Zero Labelled Data}
\textsc{Authors}:\\
Thomas Kehrenberg$^1$, Viktoriia Sharmanska$^1$, Myles Bartlett$^1$, and Novi Quadrianto$^1$ \\
\textsc{Affiliations}:\\
$^1$ Predictive Analytics Lab (PAL), University of Sussex, Brighton, UK\\
\textsc{Conference}:\;\; Submitted to \textit{Internation Conference on Machine Learning} (ICML), 2021 \\
% \textsc{DOI}:\;\;10.3389/frai.2020.00033
\textsc{Note}:\;\; The appendix has been included as section~\ref{sec:zsf-appendix}.

@@

\section{Related work.}
We describe related work in two areas: zero-shot learning and semi-su\-per\-vi\-sed learning.
%and disentangled representation learning.
